\  

The most important statistical output from Anova as R formatted objects.  
\  

::: {.panel-tabset}
# Model
```{r, eval=TRUE, include=TRUE, echo =TRUE, child='the_model.qmd'}
```

# Hypothesis
```{r, eval=TRUE, include=TRUE, echo =TRUE, child='hypothesis.qmd'}
```

# User election
## Selected variable and rol
```{r, eval=TRUE, include=TRUE, echo=FALSE}

my_df <- df_selected_vars
kable(my_df, format = "html", caption = "") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```

## Alpha and confidence values
```{r, eval=TRUE, include=TRUE, echo=FALSE}

my_df <- df_alpha_confidence
kable(my_df, format = "html", caption = "") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```

## Amount of data to analysis
```{r, eval=TRUE, include=TRUE, echo=FALSE}

my_df <- df_show_n
kable(my_df, format = "html", caption = "") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```


# Anova Table

## 1) Anova Table (Class Room format)
```{r, eval=TRUE, include=TRUE, echo=FALSE}
knitr::asis_output("This is the table format detailed in the bibliography.")

my_df <- df_table_anova_mod
kable(my_df, format = "html", caption = "") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```


## 2) Anova Table (R format)
```{r, eval=TRUE, include=TRUE, echo=FALSE}
knitr::asis_output("The original R output does not contain the Source of Variation column, and it does not detail the row for the total source of variation.")

my_df <- df_table_anova
kable(my_df, format = "html", caption = "") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```






# Tukey Test

## 1) Tukey Test (Class Room format)
```{r, eval=TRUE, include=TRUE, echo=FALSE}
knitr::asis_output("This is the table format detailed in the bibliography.")

my_df <- df_tukey_table
kable(my_df, format = "html", caption = "") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```


## 2) Full info from Tukey (R format)
```{r, eval=TRUE, include=TRUE, echo=FALSE}
knitr::asis_output("The Tukey table is only one part of all the information contained within the Tukey test.  
                   The Tukey test contains more details that may be relevant, such as the honest significant difference (HSD).")

```
```{r , eval=TRUE, include=TRUE}
tukey01_full_groups
```

## 3) Pairs comparation from Tukey test (R format)
```{r, eval=TRUE, include=TRUE, echo=FALSE}
knitr::asis_output("Internally, the Tukey test performs t-tests between all possible pairs of factor levels.  
                   In each t-test, a p-value is obtained with which decisions are made. All pairs are detailed below.")
```
```{r , eval=TRUE, include=TRUE}
tukey02_full_pairs
```

## 4) Special plot for Tukey test
```{r, eval=TRUE, include=TRUE, echo=FALSE}
knitr::asis_output("The means of each factor level are detailed with the standard error derived from the model.  
                   The statistical groups from the Tukey test are detailed for each factor level.")
```
```{r , eval=TRUE, include=TRUE}
plot007_factor
```


## 5) Tukey Test table (R format)
```{r, eval=TRUE, include=TRUE, echo=FALSE}
knitr::asis_output("This is the original R output for the Tukey test.
                    The output differs slightly from what is detailed in the bibliography.")
```
```{r, eval=TRUE, include=TRUE, echo=FALSE}

my_df <- df_tukey_original_table
kable(my_df, format = "html", caption = "") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)
```


# Requeriments
```{r cod03, eval=TRUE, include=TRUE, echo =TRUE, child='file00_03_requeriments.qmd'}
```
# Plots - Raw Data
```{r cod04, eval=TRUE, include=TRUE, echo =TRUE, child='file00_04_data_raw_plots.qmd'}
```
# Plots - Residuals
```{r cod05, eval=TRUE, include=TRUE, echo =TRUE, child='file00_05_residuals_raw_plots.qmd'}
```

# Decision Plan
```{r eval=TRUE, include=TRUE, echo =TRUE, child='file00_05_Decision.qmd'}
```

# Data Analysis (Step by step)
```{r eval=TRUE, include=TRUE, echo =TRUE, child='file00_05_StepByStep.qmd'}
```

# FAQs
```{r cod08, eval=TRUE, include=TRUE, echo =TRUE, child='file00_08_FAQ.qmd'}
```

:::
