

## Decision-Making Process in ANOVA
The ANOVA test is specifically performed to make decisions.  
The decision-making process has a set of sequential steps, in a particular order.  
- Step 01: Control over the response variable.  
- Step 02: Verification of the normality requirement of the residuals.  
- Step 03: Verification of the homogeneity of variances requirement.  
- Step 04: Interpretation of the ANOVA test.  
- Step 05: Interpretation of the Tukey test.  


### Step 01: Control over the response variable.  
De la estadística descritiva buscamos los valores mínimo y máximos de la variable respuesta par cada nivel del factor.  
Esto es acción que permite detectar posibles errores de tipeo realizados en nuestro dataset. El control solo puede ser llevado a cabo en aquellos contextos en los cuales se tiene noción de lo que podría ser un valor imposible para la variable. 
Si se trabaja sin un marco de límite para la variable respuesta, deberá asumirse que los valores mínimos y máximos son válidos y se continúa con el siguiente paso.

```{r}
#| warning: false
#| echo: false

my_df <- df_vr_position_levels
kable(my_df, format = "html", caption = "") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```


### Step 02: Verification of the normality requirement of the residuals.  
```{r}
#| warning: false
#| echo: false
nombres_aver <- c("test_residuals_normality")
aver <- mget(nombres_aver)
aver 

knitr::asis_output(phrase_shapiro_selected)
```


### Step 03: Verification of the homogeneity of variances requirement.  
```{r}
#| warning: false
#| echo: false
nombres_aver <- c("test_residuals_homogeneity")
aver <- mget(nombres_aver)
aver 
knitr::asis_output(phrase_bartlett_selected)
```

### Step 04: Interpretation of the ANOVA test.  
```{r}
#| warning: false
#| echo: false
my_df <- df_table_anova_mod
kable(my_df, format = "html", caption = "") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

knitr::asis_output(phrase_requeriments_selected)
knitr::asis_output(phrase_anova_selected)

```

### Step 05: Interpretation of the Tukey test.  
```{r}
#| warning: false
#| echo: false
my_df <- df_tukey_table
kable(my_df, format = "html", caption = "") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = FALSE)

```


```{r, eval=TRUE, include=TRUE, echo=FALSE}
knitr::asis_output("The means of each factor level are detailed with the standard error derived from the model.  
                   The statistical groups from the Tukey test are detailed for each factor level.")
```
```{r , eval=TRUE, include=TRUE}
plot007_factor
```

